Gafo-cc visuals

### 2023-10-24 analysis/gafo-cc-visuals.Rmd
update data

```{r}
data <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  mutate(community = recode(community,
                            akure = "akure (nigeria)",
                            leipzig = "leipzig (germany)",
                            `hai||om` = "hai||om (namibia)",
                            khwe = "khwe (namibia)",
                            windhoek = "windhoek (namibia)",
                            stanford = "stanford (usa)",
                            chimfunshi = "chimfunshi (sambia)",
                            mexico = "ocuilan (mexico)",
                            plymouth = "plymouth (uk)",
                            beijing = "beijing (china)", 
                            india = "pune (india)",
                            buenos_aires = "buenos aires (argentina)",
                            auckland = "auckland (new zealand)",
                            turkey = "malatya (turkey)"))
```

@@

```{r}
data%>%
  group_by(community,subjid, ageinyears)%>%
  summarise(impr = mean(abs(clickdistfromtargetcenterx)))%>%
  ggplot(aes(x = ageinyears, y = impr, col = community))+
  geom_point(alpha = .25)+
  geom_smooth(method = "glm")+
  scale_color_manual(name = "Community", values = colors)+
  ylim(0,1000)+
  facet_wrap(~community)+
  labs(x = "Age (in years)", y ="Imprecision (average click distance from target)")+
  scale_x_continuous(breaks = 2:8)+
  theme_minimal()+
  theme(legend.position = "right")

>>>>

```{r}
data <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  mutate(community = recode(community,
                            akure = "akure (nigeria)",
                            leipzig = "leipzig (germany)",
                            `hai||om` = "hai||om (namibia)",
                            khwe = "khwe (namibia)",
                            windhoek = "windhoek (namibia)",
                            stanford = "stanford (usa)",
                            chimfunshi = "chimfunshi (sambia)",
                            mexico = "ocuilan (mexico)",
                            plymouth = "plymouth (uk)",
                            beijing = "beijing (china)", 
                            india = "pune (india)",
                            buenos_aires = "buenos aires (argentina)",
                            auckland = "auckland (new zealand)",
                            turkey = "malatya (turkey)",
                            bandongo = "bandongo (rep. congo)",
                            bayaka = "bayaka (rep. congo)"))
```

@@

```{r}
data%>%
  group_by(community,subjid, ageinyears)%>%
  summarise(impr = mean(abs(clickdistfromtargetcenterx)))%>%
  ggplot(aes(x = ageinyears, y = impr, col = community))+
  geom_point(alpha = .25)+
  geom_smooth(method = "glm")+
  scale_color_manual(name = "Community", values = colors)+
  ylim(0,1000)+
  #facet_wrap(~community)+
  labs(x = "Age (in years)", y ="Imprecision (average click distance from target)")+
  scale_x_continuous(breaks = 2:8)+
  theme_minimal()+
  theme(legend.position = "right")
